Reconstructing Propositional Proofs in Type Theory

### 2017-10-24 paper/sections/conclusions-and-future-work.tex
[ paper ] none inspiration .. :S
[ paper ] two first paragraphs in the introduction.

\begin{itemize}
\item extend the proof-reconstruction presented in this paper to
  \begin{itemize}
    \item support the proposition fragment with equality of \Metis.
    \item support other \ATPs for \CPL like \name{EProver} or \name{Z3}.
    \item support \Metis first order proofs.
This development can be carried out by following the \name{EProver}
inference rules described on Kanso's Ph.D. thesis~\cite{Kanso2012}.
  \end{itemize}
\item contrasts the use of a shallow embedding instead
of the deep embedding implemented in~\cite{AgdaProp}.
\item improve some functions in Section~\ref{ssec:emulating-inferences}
\begin{itemize}
  \item by investigating the consequences of removing \clausify
inference by strengthen \canonicalize rule in Theorem~\ref{thm:canonicalize}
  \item by increasing the coverage of the \simplify rule. Since is fairly
complex its implementation in the \Metis source code, some cases could be omitted in Section~\ref{sssec:simplify}.
\end{itemize}

>>>>

\begin{itemize}
\item extend the proof-reconstruction presented in this paper to
  \begin{itemize}
    \item support the proposition fragment with equality of \Metis.
    \item support other \ATPs for propositional logic like \name{EProver} or \name{Z3}.This development can be carried out by following the \name{EProver}
description on Kanso's Ph.D. thesis~\cite{Kanso2012}.
    \item support \Metis first order proofs.

  \end{itemize}
\item contrasts a shallow embedding instead
of the deep embedding implemented in~\cite{AgdaProp} to reconstruct proofs.
\item improve some functions in Section~\ref{ssec:emulating-inferences}
\begin{itemize}
  \item by investigating the consequences of removing \clausify
inference by strengthen \canonicalize rule in Theorem~\ref{thm:canonicalize}
  \item by increasing the coverage of the \simplify rule. Since is fairly
complex its implementation in the \Metis source code, some cases could be omitted in Section~\ref{sssec:simplify}.
\end{itemize}

### 2017-10-24 paper/sections/introduction.tex
[ paper ] two first paragraphs in the introduction.

% During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems. One of the major achievements of this field are the automatic
% theorem provers (henceforth ATPs).

% At the beginning in its development, the main goal was prove automatically
% problems in different logics (\eg, first-order logic, high-order logic).
% Nowadays, they continuing extending its support, performance and precision
% in their deductive methods. To guarantee the validity of their methods,
% many ATPs has been opted to include proofs in their output.
% Nevertheless, it has been argued that some of their deductions are not
% valid even in delivering a proof. One of the reason to say that is
% the discover of bugs in ATPs that outputs unsound proofs.

% This problem to verify proofs delivered by ATPs is a non-trivial task
% and involves an in-depth understanding of the algorithms in the \ATP.

% The proof-reconstruction problem aim to solve this issue.
% One way to address this problem is using another major system in this field, the proof assistants.

@@

% To begin with the proof-reconstruction, it is
% necessary to have a proof from the \ATP in a consistent
% format, that is, a full script describing step-by-step
% with exhaustive details and without ambiguities, the derivation to
% get the that proof. But this is a strong requirement and its the main obstacle we found with \Metis proofs.
% The reader should bear in mind that the study is based on
% reverse engineering about \Metis.

@@

% This task is non-trivial since it depends on the
% integration between two complex systems.

@@

% % Since the formalism of the source (the evidence
% % generated by the \ATP) is not necessarily the same logic in the
% % target, the reconstruction turns out to be a ``reverse engineering''
% % task.

@@

 These
% programs are relevant not only because it helps to spread their
% usage but they also increase the confidence of their users about
% their algorithms and their correctness (see, for example, bugs in
% \ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
% \cite{Kanso2012}).
% We mention some of these tools in Section~\ref{sec:related-work}.

>>>>

Reconstructing and verifying proofs delivered by automatic theorem provers
(henceforth ATP) are non-trivial tasks.
In the last decades, \ATPs is fast becoming a key instrument in 
different disciplines (\eg verifying cryptographic protocols for information security) and researchers have shown an increased interest to prove the validity of the deduction algorithms.
One reason to say that are the bugs found in many ATPs.
For that reason, in order to give confidence to the user of these systems,
many ATPs has started to include in their outputs, the proofs of the
conclusion. However, existing research recognizes that in many cases these proofs encode non-trivial reasoning
hard to reconstruct them and therefore to verify them.

Hence proof-reconstructing becomes a reverse engineering task
in which the source, the proof, and its quality play an important role.
To begin with the proof-reconstruction, it is necessary to have
the proof of the \ATP in a consistent format, that is, a full script 
describing step-by-step with exhaustive details and without ambiguities, the 
derivation to get the actual proof.  
For classical propositional logic (henceforth \CPL), from a list of at least forty\footnote{\ATPs 
available from the web
service \name{SystemOnTPTP} of the TPTP World.} \ATPs, just a few
provers were able to deliver proofs and fewer like \name{EProver} or \Metis 
replied the proof in an admissible file format.

-----

% One approach to address the problem mentioned above
% consists of use a proof assistant as the proof checker.
% In this direction, we describe the usage of a proof assistant in type theory
% to reconstruct proofs delivered by \Metis prover.

% To guarantee the validity of their methods,
% many ATPs has been opted to include proofs in their output.

% The problem address in this paper concern about justifying such proofs.

% One approach to address  these tasks could be use a proof assistant
% to verify the reply of the ATP.

% % During the last decades, the research field of automated reasoning has been experimenting a growth in the development of new methods, tools, and systems. One of the major achievements of this field are the automatic
% % theorem provers (henceforth ATPs).

% At the beginning in its development, the main goal was prove automatically
% problems in different logics (\eg, first-order logic, high-order logic).
% Nowadays, they continuing extending its support, performance and precision
% in their deductive methods.

% Nevertheless, it has been argued that some of their deductions are not
% valid even in delivering a proof.

% This problem to verify proofs delivered by ATPs is a non-trivial task
% and involves an in-depth understanding of the algorithms in the \ATP.
% The proof-reconstruction is a non-trivial problem.

% The proof-reconstruction is a non-trivial task since it depends on the
% integration between two complex systems.

% The proof-reconstruction problem aims to solve this issue.
% One way to address this problem is using another major system in this field, the proof assistants.

@@

@@

@@

% Since the formalism of the source (the evidence
% generated by the \ATP) is not necessarily the same logic in the
% target, the reconstruction turns out to be a ``reverse engineering''
% task.

@@

%  These
% programs are relevant not only because it helps to spread their
% usage but they also increase the confidence of their users about
% their algorithms and their correctness (see, for example, bugs in
% \ATPs~\cite{Keller2013,Bohme2011,Fleury2014} and
% \cite{Kanso2012}).
% We mention some of these tools in Section~\ref{sec:related-work}.
